Overconfidence and settlement: evidence from Mexican labor courts\thanks{We would like to thank Sebastian Garcia, Isaac Meza, Diana Roman, and Monica Zamudio (``la banda pesada'' and ``los mas aca'') for superhuman research assistance. All errors are ours.}

### 2017-07-29 Paper/main.tex
updated

\begin{figure}[H]
\caption{Covariate distribution in Historical and Pilot data}
\label{covariate_distribution}
    \begin{center}
        \begin{subfigure}{0.49\textwidth}
            \caption{Continuous variables}
            \centering
            \includegraphics[width=\textwidth]{covariates_continuous.tiff}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
            \caption{Categorical variables}
            \centering
            \includegraphics[width=\textwidth]{covariates_categorical.tiff}
        \end{subfigure}
    \end{center}
    {\footnotesize \textit{Notes: } Covariate distributions for historical -used to calibrate our calculator- and pilot data. All continuous variables are plotted in logs. Color guide is the same for both variable types.}
    {\footnotesize \textit{Script: } \texttt{covariate\_plots.R}}
\end{figure}

>>>>

\begin{figure}[H]
\caption{Covariate distribution in Historical and Pilot data}
\label{covariate_distribution}
    \begin{center}
        \begin{subfigure}{0.49\textwidth}
            \caption{Continuous variables}
            \centering
            \includegraphics[width=\textwidth]{covariates_continuous.tiff}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
            \caption{Categorical variables}
            \centering
            \includegraphics[width=\textwidth]{covariates_categorical.tiff}
        \end{subfigure}
    \end{center}
    {\footnotesize \textit{Notes: } Covariate distributions for historical -used to calibrate our calculator- and pilot data. All continuous variables are plotted in logs. Color guide is the same for both variable types. Plots for continuous variables show the p-value of a Kolmogorov–Smirnov test in the subtitle. In the categorical covariates plot, we show significance of a two-sided t-test of differences in means between samples.}
    {\footnotesize \textit{Script: } \texttt{covariate\_plots.R}}
\end{figure}
